Reactor Design Compilation

### 2019-07-03 msr-list.tex
firstdraft yay

@@

@@

@@

As stated previously, the reprocessing in this design is purposefully limited in order to improve the fuel cycle's proliferation resistance.

@@

\section{Molten Salt Fast Reactor (MSFR)}
Of the reactors given in this review, this is one of the few fast reactors (the other being Terrapower's MCFR, given below).  Because such a reactor does not use a moderator, it circumvents some of the material contraints associated with degradation of the graphite moderator.  It also has a much higher breeding ratio.  This report uses a conceptual reference reactor with these characteristics \cite{rouch_preliminary_2014}:

@@

\begin{itemize}
\item A power of 3000 MWth
\item Three loops: the fuel, intermediate, and power conversion loops
\item Within the fuel circuit, there is a total salt volume of 18 cubic meters
	\begin{itemize}
	\item The fuel salt is lithium fluoride and actinide fluoride, with the mol\% of the actinide fluorides is assumed to be a fixed 22.5 mol\%
	\end{itemize}
\item Within the core, there is a fertile isotope blanket region, composed of a $LiF - ThF_4$ blend that has a concentration of $ThF_4$ of 22.5 mol\%
\item The blanket serves as the radial reflectors, to protect the reactor vessel.  On the top and bottom, there are reflectors made of nickel-based alloys.  This particular report also assumes this alloy will absorb 99\% of incoming neutrons.
\item The design initially used a very simple cylindrical geometry for the core, but by the time the report was written, the study moved on to more realistic, and complicated geometries.
	\begin{itemize}
	\item The first geometry is referred to as Geometry I.  The radial core walls are curved, along with the top reflector.  The bottom reflector is flat
	\item The second Geometry, Geometry II, features symmetrically curved walls within the core.  Both this and Geometry I are given in \ref{fig10} below.
	\end{itemize}
\item Helium sparging is assumed, but because its impact and the thermal-hydraulic properties was deemed neglible, it is neglected in calculations
\end{itemize}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & 100-0 \\
\hline
Coolant & \makecell{As fuel salt, without\\fuel isotopes.} \\
\hline
Moderator & No moderator \\
\hline
Fuel Composition & 8, 9 \\
\hline
\end{tabular}
\end{center}

In a separate report, \cite{doligez_coupled_2014} , a reactor with the same nominal power, and actinide mol\%.   While \cite{rouch_preliminary_2014} is focused on the thermal-hydraulic facets of an MSFR, \cite{doligez_coupled_2014} provides more in-depth information about the sort of fuel salt composition used in its reference model, and includes information on the reprocessing within the reference MSFR.

@@

\end{itemize}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msre-proc.png}
  \captionof{figure}{A diagram of the fuel-processing cell of the MSRE}
  \label{fig:figA}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msre-offgas.png}
  \captionof{figure}{The off-gas system of the MSRE}
  \label{fig:figB}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msbr-proc.png}
  \captionof{figure}{Material Flow in the MSBR Fuel-Processing Cell}
  \label{fig:figC}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msbr-offgas.png}
  \captionof{figure}{The off-gas system in the MSBR}
  \label{fig:figD}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msdr-overview.png}
  \captionof{figure}{An overview of the fuel processing in the MSDR design}
  \label{fig:figE}

\end{figure}\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msdr-offgas.png}
  \captionof{figure}{The MSDR's off-gas system}
  \label{fig:figF}
\end{figure}

@@

As stated previously, the reprocessing in this design is purposefully limited in order to improve the fuel cycle's proliferation resistance.  The desig includes an off-gas system, which will remove gaseous fission products.  Aside from this, however, the only other treatment the fuel recieves is what is necessary to keep oxygen-contamination to a minimum, and to maintain the proper levels of fissile isotopes within the fuel.  The DMSR does not include the liquid-metal reduction-extraction commonly seen in previous designs, and does not, at any point, separate protactinium.  The design assumes noble metals will leave the fuel by plating out on the piping.

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/dmsr-proc.png}
  \captionof{figure}{The diversion of salt to the off-gas system}
  \label{fig:figG}
\end{figure}

@@

\section{Molten Salt Fast Reactor (MSFR)}
Of the reactors given in this review, this is the only one using the fast spectrum (certainly, other fast-MSRs exist, but may not necessarily be interesting from a fuel-processing stand point).  Because such a reactor does not use a moderator, it circumvents some of the material contraints associated with degradation of the graphite moderator.  It also has a much higher breeding ratio.  This report uses a conceptual reference reactor with these characteristics \cite{rouch_preliminary_2014}:

@@

\begin{itemize}
\item Three loops: the fuel, intermediate, and power conversion loops
\item Within the fuel circuit, there is a total salt volume of 18 cubic meters
	\begin{itemize}
	\item The fuel salt is lithium fluoride and actinide fluoride, with the mol\% of the actinide fluorides is assumed to be a fixed 22.5 mol\%
	\end{itemize}
\item Within the core, there is a fertile isotope blanket region, composed of a $LiF - ThF_4$ blend that has a concentration of $ThF_4$ of 22.5 mol\%
\item The blanket serves as the radial reflectors, to protect the reactor vessel.  On the top and bottom, there are reflectors made of nickel-based alloys.  This particular report also assumes this alloy will absorb 99\% of incoming neutrons.
\item The design initially used a very simple cylindrical geometry for the core, but by the time the report was written, the study moved on to more realistic, and complicated, geometries.
	\begin{itemize}
	\item The first geometry is referred to as Geometry I.  The radial core walls are curved, along with the top reflector.  The bottom reflector is flat
	\item The second Geometry, Geometry II, features symmetrically curved walls within the core.  Both this and Geometry I are given in \ref{fig10} below.
	\end{itemize}
\item Helium sparging is assumed, but because its impact and the thermal-hydraulic properties was deemed neglible, it is neglected in calculations
\end{itemize}

@@

In a separate report, \cite{doligez_coupled_2014} , a reactor with the same nominal power, and actinide mol\% is studied.   While \cite{rouch_preliminary_2014} is focused on the thermal-hydraulic facets of an MSFR, \cite{doligez_coupled_2014} provides more in-depth information about the sort of fuel salt composition used in its reference model, and includes information on the reprocessing within the reference MSFR.

@@

\end{itemize}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & 100-0 \\
\hline
Coolant & \makecell{As fuel salt, without\\fuel isotopes.} \\
\hline
Moderator & No moderator \\
\hline
Fuel Composition & 8, 9 \\
\hline
\end{tabular}
\end{center}

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msfr-proc.png}
  \captionof{figure}{Fuel processing in the MSFR}
  \label{fig:figH}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[height=.5\textheight]{figures/msfr-offgas.png}
  \captionof{figure}{The off-gas system of the MSFR}
  \label{fig:figI}
\end{figure}
